\chapter*{Abstract}


    \paragraph*{}
        In small to large metropolitan cities alike, finding parking is a principal problem.\\
        Over population of major cities in Pakistan means high density of vehicles which the city cannot accommodate to begin with. This leads to lack of parking spots which in turn make parkers spend their valuable time to find a spot, increase their fuel consumption and contribute to traffic congestion.
    
    \paragraph*{}
        To tackle this problem, we came up with the idea of an app with an inbuilt map that shows parking spots all around the city to help drivers find parking spots quickly, saving time and fuel. The app will also show open parking spots close to drivers where they can easily park and also show the route to these spots. Drivers can also see how much fuel it will take to reach said spot. Since the available parking spots are visible on the map, drivers can even pre-book the spots beforehand.
        
    \paragraph*{}
        The project aims to provide parkers an application to find parking spots using their phone in real time and save them the trouble of looking for a parking spot manually. Meanwhile, the app gives the parking provider an opportunity to run a small business by putting their unused parking spot(s) up for sale. Furthermore, the project aims to provide residents who own a car but do not have a suitable parking spot near their home or residents who have trouble finding a parking spot near their workplace, a long-term parking solution by giving them the option to purchase a parking spot nearby.