\chapter{Related Work}
    
    \paragraph*{}
    To provide parking spots it is absolutely necessary to rely on either people or sensors. If the application is dependent on people it must either implement a peer to peer system like \textbf{Parkour} or use a smart phone to provide the parking spots. If the application is dependent on sensors, it must be able to provide the parking spots
    without the need of people.

    \paragraph*{}
    The other method of determined the parking spots is to use a combination of sensors and people. This is called \textbf{Sensor-based Parking} \cite{cai2015implementation} This type of methodology uses both the sensor and data from people to accurately predict of the spots are empty.

    
    \paragraph*{}
    Parking Spots can also be determined using data from the general public. This is called \textbf{Crowd-Sourced Parking} \cite{mitsopoulou2017efficient} This type of methodology uses people to verify if the parking spots are indeed empty.
    
    
    
    \paragraph*{}
    One unique method of determining if parking spots were empty or occupied was through the use of ultrasonic sensors \cite{park2008parking}. This method was found to be the most accurate and efficient method of determining if parking spots were empty or occupied without entailing the heavy cost of image recognition based parking. 
    

    \paragraph*{}
    The most effective method of determining the parking without relying on people is by using some sort of image recognition. This is called \textbf{Image-Detection-based Parking} \cite{yusnita2012intelligent} This is not only very expensive to implement but also comes with it's challenges of accurate image detection.
    
    \paragraph*{}
    \textbf{Parkour} uses peer to peer communication to determine the parking spots. This is a peer to peer system that is implemented using a smart phone. This is a system that is designed to be used by people to communicate with each other.
    


