\chapter{Testing and Evaluation}

    \section{Evaluation}
    \paragraph*{}
    Parkour will be a lightweight, reactive and responsive Application that will perform optimally on low-tier to high-tier mobile devices, including smartphones and tablets. The application will be tested on a wide range of smartphones with throttling to ensure a smooth and reactive experience. The User Experience in terms accuracy and responsiveness will be ensured because of the Application being a Single-Page App (SPA). Information on the application will be displayed and updated seamlessly without hindering User actions.


    \paragraph*{}
    Parkour ensures safe and secure User Authentication using Session Tokens and Password\\ Encryption. Each User will be awarded a Session Token through which their session will remain logged in. All sensitive information of a User is encapsulated and hidden from other users, and such information is only displayed on the Application’s Interface by prior approval of the User. User Authentication will be done on the basis of Username, Phone Number and Password provided by the User.

    \section{Testing}
    \paragraph*{}
    The Parkers may find the exact parking spot location of the spot shown on the map and end up parking the car there without paying. The app does its best to prevent this and show only some details of the spot and the rest of the information is available after booking the spot. 
    Parkour assumes the seller lists the spot that is in front of their property boundary or within their property. It also assumes that the spot is: i) at no parking zone, ii)  any area that will cause inconvenience to residents and other drivers, iii) illegal spots. 

    \paragraph*{}
    Parkour provides a platform that provides a way for drivers to find parking spots listed by sellers. However, these spots must be self-managed by the seller. In case of any loss, or harmful activity, Parkour will not be responsible. However, Parkour provides customer support service, ticketing/reporting system, a penalty system, and rate review system, to help the users of our app.
